\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-12 tex/paper.tex
save

    \begin{tikzpicture}[shorten >= 1pt, ->, node distance=\layersep,scale=.8]
    \tikzstyle{neuron} = [circle, minimum size=0.25cm, draw=black!30, line width=0.3mm, fill=white]

@@

    \node[above] at (12.75,-2.5) {$\mu(f(X;\theta_f))$};
    \path[-o, shorten >= 0pt] (11,-2.5) edge (14,-2.5);
    \node[above] at (12.75,-3.5) {$\sigma(f(X;\theta_f))$};
    \path[-o, shorten >= 0pt] (11,-3.5) edge (14,-3.5);

@@

    \caption{Architecture for the adversarial training of a binary classifier $f$ against a continuous parameter $Z$.}
    \label{fig:architecture}
\end{figure*}

>>>>

    \begin{tikzpicture}[shorten >= 1pt, ->, node distance=\layersep,scale=.85]
    \tikzstyle{neuron} = [circle, minimum size=0.25cm, draw=black!30, line width=0.3mm, fill=white]

@@

    \node[above] at (12.75,-2.5) {$\mu_{\theta_r}(f(X;\theta_f))$};
    \path[-o, shorten >= 0pt] (11,-2.5) edge (14,-2.5);
    \node[above] at (12.75,-3.5) {$\sigma_{\theta_r}(f(X;\theta_f))$};
    \path[-o, shorten >= 0pt] (11,-3.5) edge (14,-3.5);

@@

    \caption{Architecture for the adversarial training of a binary classifier $f$ against a continuous parameter $Z$. \glnote{Shall we also illustrate the losses?}}
    \label{fig:architecture}
\end{figure*}
